---
title: "2023-09-14_Hypothesis1_MultilevelModel"
date: "`r Sys.Date()`"
output: 
  html_document: 
    theme: cosmo
    toc: yes
    toc_float: yes
---

**Attentional Biases in OCD**  
**Script Part II / ?**  
**Date: 24.07.2024**  
**Version: Version 2**  

# Description
This is the main analysis file of hypothesis 1 of the 044_EYE project on Attentional Biases in OCD. This script includes the multilevel model that aims to test the main hypotheses. Furthermore, this script contains tests of the assumptions of multilevel models as well as descriptive plots. 

## Hypotheses
### 1.) Vigilance Bias: 
Patients with *OCD* and patients with *spider phobia* attend to *idiosyncratic disorder-relevant material faster* than they do to *neutral* or *negative* material (vigilance bias), as indicated by the entry time to the corresponding region of interest. 
*Healthy participants* will *not show a bias* towards disorder-relevant stimuli compared to negative or neutral stimuli.

### 2.) Maintenance Bias:
#### a.	
Patients with *OCD* look at *idiosyncratic OCD-relevant material longer* compared to *neutral* or *negative* material (maintenance bias). 
#### b.	
Patients with *OCD* will show a *more pronounced maintenance bias* compared to *healthy* participants and, with regard to *idiosyncratic disorder-specific material*, compared to patients with *spider phobia*.

### 3.) Attentional Control
#### Subjective Measure
##### a.	
In patients with *OCD* and patients with *spider phobia*, there will be a *positive association* between *vigilance bias* and *attentional control* as measured by the self-report questionnaire (Attentional Control Scale). This means the lower the attentional control, the faster patients with OCD or spider phobia will look at OCD-relevant or spider-relevant material, respectively, compared to negative or neutral material.
##### b.	
In patients with *OCD*, there will be a *negative association* between the *maintenance bias* and *attentional control* as measured by the self-report questionnaire (Attentional Control Scale). This means the lower the attentional control, the longer patients will look at idiosyncratic OCD-relevant material compared to negative or neutral material.

####Objective Measure
##### c.	
In patients with *OCD* and patients with *spider phobia*, there will be a positive association between *vigilance bias* and *attentional control* as measured by the objective measure (AX-CPT).
##### d.	
In patients with *OCD*, there will be a *negative association* between the *maintenance bias* and *attentional control* as measured by the objective measure (AX-CPT).

### 4.) Stress 
The induction of *stress* significantly increases the *maintenance bias* in patients with *OCD* (state-level). This means that patients with OCD will *look at OCD-relevant material for longer* after the stress induction than before the stress induction.

**Set Working Directory**
```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "/Volumes/109-psy-kp-study/044_EYE")
```

**Install Packages**
```{r install packages, message=F, warning=F, include=F}
# install.packages("ROCR")
# install.packages("lavaan")
# install.packages("psych")               # for basic calculations
# install.packages("foreign")             # xxx
# install.packages("ggplot2")             # for figures
# install.packages("car")                 # xxx
# install.packages("corpcor")             # for correlations
# install.packages("Hmisc")               # xxx
# install.packages("polycor")             # xxx
# install.packages("apaTables")           # for exporting tables according to APA style
# install.packages("QuantPsyc")           # xxx
# install.packages("effsize")             # xxx
# install.packages("tidyverse")           # for transforming data
# install.packages("readxl")              # for loading and exporting datasets
# install.packages("writexl")             # for loading and exporting datasets
# install.packages("bannerCommenter")     # for section headers
# install.packages("reshape2")            # for reshaping datasets
# install.packages("responsePatterns")    # for check of response patterns
# install.packages("corrplot")            # for correlation tables
# install.packages("gsubfn")              # for subsetting strings
# install.packages("data.table")          # for creating data tables
# install.packages("RColorBrewer")        # for colours in plots
# install.packages("pals")                # for colours in plots
# install.packages("devtools")
# install.packages("usethis")
# install.packages("lavaan")              # required to run SEMs
# install.packages("lavModel")            # required to run SEMs
# install.packages("ROCR")                # required to create ROC curves
# install.packages("hdf5r")
# install.packages("edfReader")           # required to read edf files
# install.packages("githubinstall")       # required to install packages from github
# install.packages("eyelinker")           # eyelink specific package
# install_github("alexander-pastukhov/eyelinkReader")                 # eyelink specific package
# install_github("aleksandernitka/EyeTracking_Tobii_VAS_IOHUB")  # eyelink specific package
# install.packages("gaze_analysis.R")     # for gaze analyses
# install.packages("report")              # to report results of anova
# install.packages("gazeR")                 # to preprocess eyetracking data
# install.packages("janitor")
# install.packages("multcomp")            # for multiple comparisons
# install.packages("lmerTest")
# install.packages("JuliaCall")
```

**Load Packages**
```{r load packages, message=F, warning=F, include=F}
library("ROCR")
library("lavaan")
library("psych")
library("foreign")
library("ggplot2")
library("car")
library("corpcor")
library("Hmisc")
library("polycor")
library("apaTables")
library("QuantPsyc")
library("effsize")
library("tidyverse")
library("readxl")
library("writexl")
library("bannerCommenter")
library("reshape2")
library("responsePatterns")
library("corrplot") 
library("gsubfn")
library("purrr")
library("data.table")
library("RColorBrewer")
library("pals")
library("dplyr")
library("edfReader")
library("devtools")
library("usethis")
library("lavaan")
library("ROCR")
library("githubinstall")
library("hdf5r")
# library("eyelinkReader")
library("stats")
library("ggplot2")
library("tidyr")
library("report")
# library("gazer")
library("janitor")
library("lme4")
library("multcomp")
library("lmerTest")
library(JuliaCall)
```

**Define the Colour Scheme**
```{r colour scheme, message=F, warning=F, include=F}
color1 <- "#003C6799"
color2 <- "#CD534C99"
color3 <- 'lightgoldenrod1'
color4 <- "darkseagreen"
```

# Install Julia
```{r install julia}
#install.packages(c("lme4","juliaCall","multcomp","dplyr"))
library(JuliaCall)
options(JULIA_HOME = "/Applications/Julia-1.10.app/Contents/Resources/julia/bin") # need to define the path for my Mac to resolve bug
j = julia_setup(installJulia = TRUE)
```

## Install Julia Packages
```{julia install julia packages, echo = F}
using Pkg
Pkg.activate(".")
Pkg.add(["MixedModels","JellyMe4","RCall"])
  
ENV["LMER"] ="lmerTest::lmer"
```


# Load Data 
```{r load data}
# data_dwelltime = read.csv("../data/2024-07-23_data-dwelltime.csv")
# data_entrytime = read.csv("../data/2024-07-23_data-entrytime.csv")
data_dwelltime = read.csv("06_Results/02_Hauptstudie/FilesAnalysis/data_dwelltime_OA.csv")
data_entrytime = read.csv("06_Results/02_Hauptstudie/FilesAnalysis/data_entrytime_OA.csv")

data_entrytime$participant = data_dwelltime$participant

data_entrytime$rt = data_entrytime$first_entry_time_left

ix_right = is.na(data_entrytime$first_entry_time_left)
data_entrytime$rt[ix_right] = data_entrytime$first_entry_time_right[ix_right]

data_entrytime$response = data_entrytime$first_entry_ID_left
data_entrytime$response[ix_right] = data_entrytime$first_entry_ID_right[ix_right]

# stim effects
data_entrytime$ocd_left = data_entrytime$stim_ocd == -1
data_entrytime$ocd_right = data_entrytime$stim_ocd == 1

data_entrytime$pho_left = data_entrytime$stim_pho == -1
data_entrytime$pho_right = data_entrytime$stim_pho == 1

data_entrytime$neg_left = data_entrytime$stim_neg == -1
data_entrytime$neg_right = data_entrytime$stim_neg == 1

data_entrytime$looked_right = is.na(data_entrytime$first_entry_ID_left)
ir = data_entrytime$looked_right
il = !data_entrytime$looked_right
data_entrytime$looked_at = 'neutral'
data_entrytime$not_looked_at = 'neutral'

ix = (il & data_entrytime$pho_left) | (ir & data_entrytime$pho_right)
data_entrytime$looked_at[ix] = "pho"

ix = (il & data_entrytime$ocd_left) | (ir & data_entrytime$ocd_right)
data_entrytime$looked_at[ix] = "ocd"

ix = (il & data_entrytime$neg_left) | (ir & data_entrytime$neg_right)
data_entrytime$looked_at[ix] = "neg"

ix = (ir & data_entrytime$pho_left) | (il & data_entrytime$pho_right)
data_entrytime$not_looked_at[ix] = "pho"

ix = (ir & data_entrytime$ocd_left) | (il & data_entrytime$ocd_right)
data_entrytime$not_looked_at[ix] = "ocd"

ix = (ir & data_entrytime$neg_left) | (il & data_entrytime$neg_right)
data_entrytime$not_looked_at[ix] = "neg"
```

# Hypothesis 1: Maintenance Bias 
*From Complex to Simple Multilevel Models*
## Creagte Models
```{r create julia models for H1}
#j $assign("form", formula(mlm_dwelltime))
j$assign("jl_data_dwelltime", data_dwelltime)
j$assign("jl_data_entrytime", data_entrytime)
julia_command("jl_data_entrytime.response .= jl_data_entrytime.response .-1")
julia_command("using MixedModels")
julia_command("using JellyMe4")

# Model 1: Most Complex Model
julia_command("h1_form_complex = @formula(dwell_diff ~ group + stim_ocd + stim_pho + stim_neg  + group&stim_ocd + group&stim_pho + group&stim_neg +
              (1 + stim_ocd + stim_pho + stim_neg | triplet)+
              (1 + stim_ocd + stim_pho + stim_neg | participant) +
              (1 + group | picture_pair_countingindex))")

# Model 2a: Triplet ZeroCorr
julia_command("h1_form_triplet_zerocorr = @formula(dwell_diff ~ group + stim_ocd + stim_pho + stim_neg  + group&stim_ocd + group&stim_pho + group&stim_neg + 
              zerocorr(1 + stim_ocd + stim_pho + stim_neg | triplet)+
              (1 + stim_ocd + stim_pho + stim_neg | participant) +
              (1 + group | picture_pair_countingindex))")

# Model 2b: Triplet and Participant ZeroCorr
julia_command("h1_form_triplet_id_zerocorr = @formula(dwell_diff ~ group + stim_ocd + stim_pho + stim_neg  + group&stim_ocd + group&stim_pho + group&stim_neg + 
              zerocorr(1 + stim_ocd + stim_pho + stim_neg | triplet)+
              zerocorr(1 + stim_ocd + stim_pho + stim_neg | participant) +
              (1 + group | picture_pair_countingindex))")

# Model 2c: Triplet, Participant and Item Effect ZeroCorr
julia_command("h1_form_triplet_id_item_zerocorr = @formula(dwell_diff ~ group + stim_ocd + stim_pho + stim_neg  + group&stim_ocd + group&stim_pho + group&stim_neg + 
              zerocorr(1 + stim_ocd + stim_pho + stim_neg | triplet)+
              zerocorr(1 + stim_ocd + stim_pho + stim_neg | participant) +
              zerocorr(1 + group | picture_pair_countingindex))")

# Model 3a: Exclude Participant
julia_command("h1_form_excl_id = @formula(dwell_diff ~ group + stim_ocd + stim_pho + stim_neg  + group&stim_ocd + group&stim_pho + group&stim_neg +
              (1 + stim_ocd + stim_pho + stim_neg | triplet)+
              (1 + group | picture_pair_countingindex))")

# Model 3b: Exclude Triplet
julia_command("h1_form_excl_triplet = @formula(dwell_diff ~ group + stim_ocd + stim_pho + stim_neg  + group&stim_ocd + group&stim_pho + group&stim_neg + 
              (1 + stim_ocd + stim_pho + stim_neg | participant)+
              (1 + group | picture_pair_countingindex))")

# Model 3c: Exclude Triplet
julia_command("h1_form_excl_item  = @formula(dwell_diff ~ group + stim_ocd + stim_pho + stim_neg  + group&stim_ocd + group&stim_pho + group&stim_neg +
              (1 + stim_ocd + stim_pho + stim_neg | triplet)+
              (1 + stim_ocd + stim_pho + stim_neg | participant))")

# Model 4a: Exclude Participant and Triplet
julia_command("h1_form_excl_triplet_id = @formula(dwell_diff ~ group + stim_ocd + stim_pho + stim_neg  + group&stim_ocd + group&stim_pho + group&stim_neg + 
              (1 + group | picture_pair_countingindex))")

# Model 4b: Exclude Triplet and Item
julia_command("h1_form_excl_triplet_item = @formula(dwell_diff ~ group + stim_ocd + stim_pho + stim_neg  + group&stim_ocd + group&stim_pho + group&stim_neg + 
              (1 + stim_ocd + stim_pho + stim_neg | participant))")

# Model 4c: Exclude Participant and Item
julia_command("h1_form_excl_id_item = @formula(dwell_diff ~ group + stim_ocd + stim_pho + stim_neg  + group&stim_ocd + group&stim_pho + group&stim_neg + 
              (1 + stim_ocd + stim_pho + stim_neg | triplet))")
```

## Hypothesis 1: Evaluate Models 
```{r evaluate julia models for H1}
# Model 1
julia_command("h1_fm_complex = fit(LinearMixedModel, h1_form_complex, jl_data_dwelltime)")

# Models 2: Zero Correlation
julia_command("h1_fm_trip_zc = fit(LinearMixedModel, h1_form_triplet_zerocorr, jl_data_dwelltime)")
julia_command("h1_fm_trip_id_zc = fit(LinearMixedModel, h1_form_triplet_id_zerocorr, jl_data_dwelltime)")
julia_command("h1_fm_trip_id_item_zc = fit(LinearMixedModel, h1_form_triplet_id_item_zerocorr, jl_data_dwelltime)")

# Models 3: Exclude One Random Effect
julia_command("h1_fm_excl_id = fit(LinearMixedModel, h1_form_excl_id, jl_data_dwelltime)")
julia_command("h1_fm_excl_triplet = fit(LinearMixedModel, h1_form_excl_triplet, jl_data_dwelltime)")
julia_command("h1_fm_excl_item = fit(LinearMixedModel, h1_form_excl_item, jl_data_dwelltime)")
  
# Models 4: Exclude Two Random Effects
julia_command("h1_fm_excl_triplet_id = fit(LinearMixedModel, h1_form_excl_triplet_id, jl_data_dwelltime)")
julia_command("h1_fm_excl_triplet_item = fit(LinearMixedModel, h1_form_excl_triplet_item, jl_data_dwelltime)")
julia_command("h1_fm_excl_id_item = fit(LinearMixedModel, h1_form_excl_id_item, jl_data_dwelltime)")
```

# Hypothesis 2: Vigilance Bias 
*From Complex to Simple Multilevel Models*
## Choice (wo Entry Time)
```{r create julia models for H2a choice}
# Model 1: Most Complex Model
julia_command("h2a_glm_form_complex = @formula(response ~ group + stim_ocd + stim_pho + stim_neg  + group&stim_ocd + group&stim_pho + group&stim_neg + 
              (1 + stim_ocd + stim_pho + stim_neg | triplet)+
              (1 + stim_ocd + stim_pho + stim_neg | participant) +
              (1 + group | picture_pair_countingindex))")

# Model 2a: Triplet ZeroCorr
julia_command("h2a_glm_form_triplet_zerocorr = @formula(response ~ group + stim_ocd + stim_pho + stim_neg  + group&stim_ocd + group&stim_pho + group&stim_neg + 
              zerocorr(1 + stim_ocd + stim_pho + stim_neg | triplet)+
              (1 + stim_ocd + stim_pho + stim_neg | participant) +
              (1 + group | picture_pair_countingindex))")

# Model 2b: Triplet and Participant ZeroCorr
julia_command("h2a_glm_form_triplet_id_zerocorr = @formula(response ~ group + stim_ocd + stim_pho + stim_neg  + group&stim_ocd + group&stim_pho + group&stim_neg + 
              zerocorr(1 + stim_ocd + stim_pho + stim_neg | triplet)+
              zerocorr(1 + stim_ocd + stim_pho + stim_neg | participant) +
              (1 + group | picture_pair_countingindex))")

# Model 2c: Triplet, Participant and Item Effect ZeroCorr
julia_command("h2a_glm_form_triplet_id_item_zerocorr = @formula(response ~ group + stim_ocd + stim_pho + stim_neg  + group&stim_ocd + group&stim_pho + group&stim_neg + 
              zerocorr(1 + stim_ocd + stim_pho + stim_neg | triplet)+
              zerocorr(1 + stim_ocd + stim_pho + stim_neg | participant) +
              zerocorr(1 + group | picture_pair_countingindex))")

# Model 3a: Exclude Participant
julia_command("h2a_glm_form_excl_id = @formula(response ~ group + stim_ocd + stim_pho + stim_neg  + group&stim_ocd + group&stim_pho + group&stim_neg + 
              (1 + stim_ocd + stim_pho + stim_neg | triplet)+
              (1 + group | picture_pair_countingindex))")

# Model 3b: Exclude Triplet
julia_command("h2a_glm_form_excl_triplet = @formula(response ~ group + stim_ocd + stim_pho + stim_neg  + group&stim_ocd + group&stim_pho + group&stim_neg + 
              (1 + stim_ocd + stim_pho + stim_neg | participant)+
              (1 + group | picture_pair_countingindex))")

# Model 3c: Exclude Triplet
julia_command("h2a_glm_form_excl_item  = @formula(response ~ group + stim_ocd + stim_pho + stim_neg  + group&stim_ocd + group&stim_pho + group&stim_neg +
              (1 + stim_ocd + stim_pho + stim_neg | triplet)+
              (1 + stim_ocd + stim_pho + stim_neg | participant))")

# Model 4a: Exclude Participant and Triplet
julia_command("h2a_glm_form_excl_triplet_id = @formula(response ~ group + stim_ocd + stim_pho + stim_neg  + group&stim_ocd + group&stim_pho + group&stim_neg + 
              (1 + group | picture_pair_countingindex))")

# Model 4b: Exclude Triplet and Item
julia_command("h2a_glm_form_excl_triplet_item = @formula(response ~ group + stim_ocd + stim_pho + stim_neg  + group&stim_ocd + group&stim_pho + group&stim_neg + 
              (1 + stim_ocd + stim_pho + stim_neg | participant))")

# Model 4c: Exclude Participant and Item
julia_command("h2a_glm_form_excl_id_item = @formula(response ~ group + stim_ocd + stim_pho + stim_neg  + group&stim_ocd + group&stim_pho + group&stim_neg + 
              (1 + stim_ocd + stim_pho + stim_neg | triplet))")


julia_command("glm_form= @formula(response ~ group + stim_ocd + stim_pho + stim_neg  + group&stim_ocd + group&stim_pho + group&stim_neg + 
              zerocorr(1 + stim_ocd + stim_pho + stim_neg | participant))")
```
## Hypothesis 2.1: Evaluate Models 
```{r evaluate julia models for H2a}
# Model 1
julia_command("h2a_glm_fm_complex = fit(MixedModel, h2a_glm_form_complex, jl_data_entrytime,Bernoulli();contrasts=Dict(:group=>DummyCoding(;base=\"healthy\")))")

# Models 2: Zero Correlation
julia_command("h2a_glm_fm_trip_zc = fit(MixedModel, h2a_glm_form_triplet_zerocorr, jl_data_entrytime,Bernoulli();contrasts=Dict(:group=>DummyCoding(;base=\"healthy\")))")
julia_command("h2a_glm_fm_trip_id_zc = fit(MixedModel, h2a_glm_form_triplet_id_zerocorr, jl_data_entrytime,Bernoulli();contrasts=Dict(:group=>DummyCoding(;base=\"healthy\")))")
julia_command("h2a_glm_fm_trip_id_item_zc = fit(MixedModel, h2a_glm_form_triplet_id_item_zerocorr, jl_data_entrytime,Bernoulli();contrasts=Dict(:group=>DummyCoding(;base=\"healthy\")))")

# Models 3: Exclude One Random Effect
julia_command("h2a_glm_fm_excl_id = fit(MixedModel, h2a_glm_form_excl_id, jl_data_entrytime,Bernoulli();contrasts=Dict(:group=>DummyCoding(;base=\"healthy\")))")
julia_command("h2a_glm_fm_excl_triplet = fit(MixedModel, h2a_glm_form_excl_triplet, jl_data_entrytime,Bernoulli();contrasts=Dict(:group=>DummyCoding(;base=\"healthy\")))")
julia_command("h2a_glm_fm_excl_item = fit(MixedModel, h2a_glm_form_excl_item, jl_data_entrytime,Bernoulli();contrasts=Dict(:group=>DummyCoding(;base=\"healthy\")))")
  
# Models 4: Exclude Two Random Effects
julia_command("h2a_glm_fm_excl_triplet_id = fit(MixedModel, h2a_glm_form_excl_triplet_id, jl_data_entrytime,Bernoulli();contrasts=Dict(:group=>DummyCoding(;base=\"healthy\")))")
julia_command("h2a_glm_fm_excl_triplet_item = fit(MixedModel, h2a_glm_form_excl_triplet_item, jl_data_entrytime,Bernoulli();contrasts=Dict(:group=>DummyCoding(;base=\"healthy\")))")
julia_command("h2a_glm_fm_excl_id_item = fit(MixedModel, h2a_glm_form_excl_id_item, jl_data_entrytime,Bernoulli();contrasts=Dict(:group=>DummyCoding(;base=\"healthy\")))")
```

## Entry Time
# QUESTION: correct that only one random effect?
```{r create julia models for h2b choice}
# Model 1: Most Complex Model
julia_command("h2b_form_complex = @formula(rt ~ group*looked_at + looked_right*group+ + 
              (1 + group | picture_pair_countingindex))")

# Model 2a: Triplet ZeroCorr
julia_command("h2b_form_item_zerocorr = @formula(rt ~ group*looked_at + looked_right*group+ + 
              zerocorr(1 + group | picture_pair_countingindex))")
```

## Hypothesis 2.1: Define Effect and Dummy Coding 
```{r define effect and dummy coding julia models for h2b}
# Model 1
julia_command("h2b_fm_complex = fit(MixedModel, h2b_form_complex, jl_data_entrytime;contrasts=Dict(
       :group=>DummyCoding(;base=\"healthy\"),:looked_right=>EffectsCoding(),:looked_at=>DummyCoding(;base=\"neutral\")));")

# Models 2a: Zero Correlation
julia_command("h2b_fm_item_zc = fit(MixedModel, h2b_form_item_zerocorr, jl_data_entrytime;contrasts=Dict(
       :group=>DummyCoding(;base=\"healthy\"),:looked_right=>EffectsCoding(),:looked_at=>DummyCoding(;base=\"neutral\")));")
```


## Hypothesis 2.1: Evaluate Models
```{r evaluate julia models for H2b}
# Model 1
julia_command("tupl_h2b_fm_complex = (h2b_fm_complex,jl_data_entrytime);")

# Transform to R
# julia_command("@rput(tupl_h2b_fm_complex);")
# julia_command("typeof(tupl_h2b_fm_complex)")

# Models 2: Zero Correlation
julia_command("tupl_h2b_fm_item_zc = (h2b_fm_item_zc,jl_data_entrytime);")

# Transform to R
# julia_command("@rput(tupl_h2b_fm_item_zc);")
# julia_command("typeof(tupl_h2b_fm_item_zc)")
```

# Test of Hypotheses Based on Multilevel Model
To establish contrast codes that directly test the hypotheses, we first code the hypotheses we want to test. Then, we fit the established effects in the contrast() function. This function allows direct inspection of effects. The p-values are estimated by the Kenward-Roger method. The p-values are unadjusted.

```{r generalised hypotheses matrices}
# Define the model comparisons to test the specific hypothesis of hypothesis 2
g = (glht(mlm_dwelltime, (c("groupocd:stim_ocd - groupocd = 0", # Patients with OCD look at idiosyncratic OCD-relevant material longer compared to neutral material (maintenance bias within group)
                            "groupocd:stim_ocd - groupocd:stim_neg = 0", # Patients with OCD look at idiosyncratic OCD-relevant material longer compared to negative material (maintenance bias within group)
                            "groupocd:stim_ocd - stim_ocd = 0", # Patients with OCD will show a more pronounced maintenance bias compared to healthy participants (maintenance bias between groups)
                            "groupocd:stim_ocd -  groupspider:stim_pho = 0" # Patients with OCD will show a more pronounced maintenance to idiosyncratic disorder-specific material compared to patients with spider phobia (maintenance bias between group)
))))

# Kenward-Roger is a more conservative method than the likelihood ratio test 
# Likelihood ratio tests always compares two models with each other 
# this is easy when the contrast is a treatment effect, but more difficult if we have three variables
# Deviation from preregistration - but this option is better, as 
# 1. Contrasts are more easily to be implemented with contest(), as we have many different contrasts and three groups that we want to compare within- and between-subjects (LR would only allow two comparisons at a time)
# 2. Kenward-Roger is more conservative than Likelihood Ratio Test
contest(mlm_dwelltime,g$linfct,joint=FALSE)#,ddf="Kenward-Roger")
```


<!-- # Trash? -->
<!-- # Hypothesis 1 -->
<!-- ```{r multilevel model} -->
<!-- data_dwelltime$group <- relevel(as.factor(data_dwelltime$group),ref = "healthy") -->

<!-- mlm_dwelltime <- lmer(dwell_diff ~ group + stim_ocd + stim_pho + stim_neg  + group:stim_ocd + group:stim_pho + group:stim_neg + -->
<!--                         (1 + stim_ocd + stim_pho + stim_neg || participant), -->
<!--                         #(1 + group | picture_pair_countingindex), -->
<!--                       data = data_dwelltime, -->
<!--                       REML=TRUE, -->
<!--                       control = lmerControl(), # default optimiser -->
<!--                       set.seed(1337)) # set the seed to replicate results -->
<!-- summary(mlm_dwelltime) -->
<!-- ``` -->

<!-- ## Extract Coefficients from LMM  -->
<!-- ```{r extract coefficients from LMM} -->
<!-- # find ID <-> group mapping -->
<!-- df = data_dwelltime %>%  -->
<!--   dplyr::select(participant, group) %>% -->
<!--   unique() -->

<!-- # extract the individual participant coefficient for the OCD stim effect -->
<!-- df$stim_ocd = coef(mlm_dwelltime)$participant$stim_ocd + coef(mlm_dwelltime)$participant$groupocd + coef(mlm_dwelltime)$participant$`groupocd:stim_ocd` -->
<!-- df -->
<!-- ``` -->

<!-- # Hypothesis 2: Analyses of Reaction Time  -->
<!-- ```{julia hypothesis 2 reaction time} -->
<!-- using RCall -->
<!-- using MixedModels -->
<!-- using JellyMe4 -->
<!-- jl_data_entrytime = @rget data_entrytime -->

<!-- rt_form= @formula(rt ~ group*looked_at + looked_right*group+zerocorr(1 +looked_at+looked_right| participant)) -->


<!-- tmp = fit(MixedModel, rt_form, jl_data_entrytime;contrasts=Dict(:group=>DummyCoding(;base="healthy"), -->
<!--                                                                 :looked_right=>EffectsCoding(), -->
<!--                                                                 :looked_at=>DummyCoding(;base="neutral"))); -->

<!-- # tupl = (tmp,jl_data_entrytime); -->
<!-- # @rput -->
<!-- (tupl); -->
<!-- ``` -->

<!-- ```{julia} -->
<!-- typeof(tpl) -->
<!-- ``` -->

<!-- ```{julia} -->
<!-- tpl = (tmp,jl_data_entrytime) -->
<!-- @rput(tpl) -->
<!-- ``` -->
<!-- ```{r} -->
<!-- library(fddm) -->
<!-- library(tidyr) -->

<!-- #j$assign("form", formula(mlm_dwelltime)) -->
<!-- j$assign("jl_data_dwelltime", data_dwelltime) -->
<!-- j$assign("jl_data_entrytime", data_entrytime) -->
<!-- julia_command("jl_data_entrytime.response .= jl_data_entrytime.response .-1") -->
<!-- julia_command("using MixedModels") -->
<!-- julia_command("using JellyMe4") -->

<!-- julia_command("form_triplet = @formula(dwell_diff ~ group + stim_ocd + stim_pho + stim_neg  + group&stim_ocd + group&stim_pho + group&stim_neg +  -->
<!--               (1 + stim_ocd + stim_pho + stim_neg | triplet)+ -->
<!--               (1 + stim_ocd + stim_pho + stim_neg | participant) + -->
<!--               (1 + group | picture_pair_countingindex))") -->
<!-- julia_command("fm_trip = fit(LinearMixedModel, form_triplet, jl_data_dwelltime)") -->



<!-- bla = function(d){ -->

<!--   #d = df[Z==z] -->
<!-- #d = data_entrytime -->


<!-- d = d%>%subset(rt>=50) -->
<!-- fit0 <- ddm(rt + response ~ 1+ocd_left+ocd_right+pho_left+pho_right+neg_left+neg_right, data = d) -->
<!-- return(data.frame(t(coef(fit0)))) -->
<!-- } -->
<!-- drift_res = data_entrytime %>% drop_na(stim_pho,stim_ocd) %>% group_by(participant,group) %>% do(bla(.)) -->


<!-- ``` -->